Implementing Real-time Transport Services over an Ossified Network

### 2016-05-22 paper.tex
Note related work
Expand Realising Transport Services

To offer a message-oriented abstraction, the boundaries between each
message must be maintained between sender and receiver. This means that a
framing mechanism is required: it is not sufficient to send each message in
a single segment, as this mapping will not necessarily be maintained by the
network. A framing marker is added to the start and end of each message
before transmission. An encoding algorithm is used to escape all occurences
of the framing marker within the message data. This process does not impact
on the data that can be sent or received by applications.

@@

This mechanism -- inconsistent retransmissions -- is visible to middleboxes
on the network that are performing payload inspection. These middleboxes
may interpret this behaviour relating to an attack. For example, a
man-on-the-side attack exhibits similar behaviour, where a malicious host
is injecting data into an existing TCP flow. As a result, our connection
may be disrupted. Honda et al. \cite{honda:2011:extend-tcp} conducted
experiments across 135 paths on the Internet, to determine support for
inconsistent retransmissions. The observed that the majority of paths
delivered inconsistent retransmissions successfully. On Port 80 (HTTP), the
original segment was delivered on 7\% of paths tested. Only one connection
reset was observed. We conducted further deployability experiments using
inconsistent retransmissions \cite{mcquistin2016hollywood}, and found that
fixed-line networks delivered inconsistent retransmissions successfully,
but that delivery of the original segment was common on cellular networks.

These deployability experiments suggest that our protocol should be
flexible: inconsistent retransmissions may not be delivered, and we should
handle reception of the original segment. If the protocol detects that
inconsistent retransmissions are not being delivered, then the mechanism
can be disabled for the connection. Further, if a connection reset occurs,
then the connection should be retried with the mechanism disabled.

@@

While further measurement studies are required to determine the
deployability of wire-visible changes to TCP (such as inconsistent
retransmissions), we have shown that we can provide all of the transport 
services needed by real-time applications, using either TCP or UDP. The
API shown in Table \ref{tab:api} is largely similar to that PR-SCTP, which
has seen real-world deployments within the WebRTC protocol, demonstrating
that we can layer these services above UDP.

However, as described in Section \ref{sec:ossification}, there are
deployability advantages to providing these services across TCP.

these services are deployed over TCP now, but have an inconvenient API that
imposes lots of work on application developers, and with higher than desired
latency. 
TCP Hollywood offers a way to fix both issues.
Brief summary.
Obviously we need to change TCP congestion control too.

@@

>>>>

To offer a message-oriented abstraction, the boundaries between each
message must be maintained between sender and receiver. This means that a
framing mechanism is required: it is not sufficient to send each message in
a single segment, as this mapping will not necessarily be maintained by the
network. A framing marker is added to the start and end of each message
before transmission. An encoding algorithm is used to escape all occurrences
of the framing marker within the message data. This process does not impact
on the data that can be sent or received by applications.

@@

This mechanism -- inconsistent retransmissions -- is visible to middleboxes
on the network that are performing payload inspection. These middleboxes
may interpret this behaviour relating to an attack. For example, a
man-on-the-side attack exhibits similar behaviour, where a malicious host
is injecting data into an existing TCP flow. As a result, our connection
may be disrupted. Honda et al. \cite{honda:2011:extend-tcp} conducted
experiments across 135 paths on the Internet, to determine support for
inconsistent retransmissions. The observed that the majority of paths
delivered inconsistent retransmissions successfully. On Port 80 (HTTP), the
original segment was delivered on 7\% of paths tested. Only one connection
reset was observed.

We conducted further deployment experiments using
inconsistent retransmissions \cite{mcquistin2016hollywood}, and found that
fixed-line networks delivered inconsistent retransmissions successfully,
but that delivery of the original segment was common on cellular networks.
\todo{expand this}

These deployment experiments suggest that our protocol should be
flexible: inconsistent retransmissions may not be delivered, and we should
handle reception of the original segment. If the protocol detects that
inconsistent retransmissions are not being delivered, then the mechanism
can be disabled for the connection. Further, if a connection reset occurs,
then the connection should be retried with the mechanism disabled.

@@

While further measurement studies are required to confirm the ability to
deploy wire-visible changes to TCP (such as inconsistent retransmissions),
we have shown that we can provide all of the transport services needed by
real-time applications, using either TCP or UDP.

Evidence that these services can be deployed above UDP exists in the form
of the WebRTC data channel \cite{}.  
\todo{expand}

\todo{also QUIC}

% The API shown in Table \ref{tab:api} is largely similar to that PR-SCTP,
% which has seen real-world deployments within the WebRTC protocol,
% demonstrating that we can layer these services above UDP.

Deployments using UDP are popular, and work well. However, as described in
Section \ref{sec:ossification}, there are also reasons for providing these 
services running over TCP. 
\todo{
  these services are deployed over TCP now, but have an inconvenient API that
  imposes lots of work on application developers, and with higher than desired
  latency. 
  TCP Hollywood offers a way to fix both issues.
  Brief summary.
  Obviously we need to change TCP congestion control too.
}

Taken together, the wide experiences with the WebRTC Data Channel and QUIC
demonstrate that the transport services necessary to support real-time
traffic could be deployed running over UDP. Our work prototyping the TCP
Hollywood protocol, and earlier measurements by Honda \emph{et al}.\
\cite{} also suggest that deployment over TCP is possible.

The challenge for the future is in combining such techniques below a common
API, so that an application can transparently switch between UDP-based and
TCP-based transport, depending on what is supported by the underlying
network. This is the promise of the TAPS API, that we have shown ought to
be feasible for real-time applications.

@@

\todo{Stephen: TCP minion; time-lined TCP}

\todo{QUIC}

\todo{SPUD}

\todo{WebRTC data channel - SCTP over UDP}

\todo{RFC6773 - DCCP over UDP}
